---
title: "Independance_exercises"
output: pdf_document
---

```{r}
#install.packages("readxl")
library("readxl")
data<-read_excel("Drive/RecapTM2S20202021.xlsx")

summary(data)
head(data)
vect<-c(4,5,6,8,9,10,14,15,17,18) #colonnes des exercices sans les globaux
asy<-c(7,11,16) #colonnes où sont indiquées les asymétries
data$Mobinfasy=factor(data$Mobinfasy, labels=c("0","1"))
data$Mobsupasy=factor(data$Mobsupasy, labels=c("0","1"))
data$Stabpelvasy=factor(data$Stabpelvasy, labels=c("0","1"))

boxplot(data[vect],main = "boxplot")

Mobinfasy<-table(data$Mobinfasy); Mobinfasy
Mobsupasy<-table(data$Mobsupasy);Mobsupasy
Stabpelvasy<-table(data$Stabpelvasy); Stabpelvasy

Mobasy=table(Mobsupasy,Mobinfasy);Mobasy
Stabmobinfasy=table(Mobinfasy,Stabpelvasy);Stabmobinfasy
Stabmobsupasy=table(Mobsupasy,Stabpelvasy);Stabmobsupasy
M=cor(Stabmobinfasy,Stabmobsupasy)
library(corrplot)
corrplot(M,method='ellipse')
```

```{r}
data<-read_excel("Drive/RecapTM2S20202021.xlsx")
head(data)
data$Mobinfasy=factor(data$Mobinfasy,labels=c("0","1"))
data$Mobsupasy=factor(data$Mobsupasy,labels=c("0","1"))
data$Stabpelvasy=factor(data$Stabpelvasy,labels=c("0","1"))
data$Mobinfasy=as.numeric(data$Mobinfasy)
data$Mobsupasy=as.numeric(data$Mobsupasy)
data$Stabpelvasy=as.numeric(data$Stabpelvasy)
head(data)
exos_asy=data[,c(7,11,16)]
M=cor(exos_asy)
corrplot(M,method='ellipse')
```

```{r}
data<-read_excel("Drive/RecapTM2S20202021.xlsx")
head(data)
exos_asy=data[,c(4,5,6,8,9,10,12,14,15,17,18)]
M<-cor(exos_asy)
corrplot(M,method='ellipse')
```

```{r}
data<-read_excel("Drive/TM2S_20212022.xlsx")
head(data)
exos_asy=data[,c(4,5,6,8,9,10,12,14,15,17,18)]
M<-cor(exos_asy)
M
corrplot(M,method='circle')
```
Here, we can see the correlation between Mobinfdroite and Mobinfgauche. That is what we were expecting. We can also see that the categories are not really linked (or correlated). The different exercises are not repetitive and each one is playing a distincly important role. We find the same results as the year before. 

Now, we are going to test if the exercises are linked between themselves. 

```{r}
#install.packages("readxl")
library("readxl")
data<-read_excel("Drive/TM2S_20212022.xlsx")
head(data)
new<-data.frame(data)
```
```{r}
Mobinfdroite=data$Mobinfdroite
Mobinfgauche=data$Mobinfgauche
Mobinfbil=data$Mobinfbil

Mobsupdroite=data$Mobsupdroite
Mobsupgauche=data$Mobsupgauche
Mobsupbil=data$Mobsupbil

Stabpelvdroite=data$Stabpelvdroite
Stabpelvgauche=data$Stabpelvgauche
Stabscap=data$Stabscapulaire
```

```{r}
#Indépendance entre catégories d'exercices : Mobinfdroite
chisq.test(Mobinfdroite,Mobinfgauche)
chisq.test(Mobinfdroite,Mobinfbil)
chisq.test(Mobinfdroite,Mobsupdroite)
chisq.test(Mobinfdroite,Mobsupgauche)
chisq.test(Mobinfdroite,Mobsupbil)
chisq.test(Mobinfdroite,Stabpelvdroite)
chisq.test(Mobinfdroite,Stabpelvgauche)
chisq.test(Mobinfdroite,Stabscap)
```
Mobinfdroite and Stabpelvdroite independent
Mobinfdroite and Stabpelvgauche independent
Mobinfdroite and Stabscap independent
```{r}
#Indépendance entre catégories d'exercices : Mobinfgauche
chisq.test(Mobinfgauche,Mobinfbil)
chisq.test(Mobinfgauche,Mobsupdroite)
chisq.test(Mobinfgauche,Mobsupgauche)
chisq.test(Mobinfgauche,Mobsupbil)
chisq.test(Mobinfgauche,Stabpelvdroite)
chisq.test(Mobinfgauche,Stabpelvgauche)
chisq.test(Mobinfgauche,Stabscap)
```
Mobinfgauche and Mobsupdroite independent
Mobinfgauche and Stabpelvdroite independent
Mobinfgauche and Stabpelvgauche independent
Mobinfgauche and Stabscap independent
```{r}
#Indépendance entre catégories d'exercices : Mobinfbil
chisq.test(Mobinfbil,Mobsupdroite)
chisq.test(Mobinfbil,Mobsupgauche)
chisq.test(Mobinfbil,Mobsupbil)
chisq.test(Mobinfbil,Stabpelvdroite)
chisq.test(Mobinfbil,Stabpelvgauche)
chisq.test(Mobinfbil,Stabscap)
```
Mobinfbil and Mobsupdroite independent
Mobinfbil and Mobsupgauche independent
Mobinfbil and Stabpelvdroite independent
Mobinfbil and Stabpelvgauche independent
Mobinfbil and Stabscap independent
```{r}
#Indépendance entre catégories d'exercices : Mobsupdroite
chisq.test(Mobsupdroite,Mobsupgauche)
chisq.test(Mobsupdroite,Mobsupbil)
chisq.test(Mobsupdroite,Stabpelvdroite)
chisq.test(Mobsupdroite,Stabpelvgauche)
chisq.test(Mobsupdroite,Stabscap)
```
Mobsupdroite and Stabpelvdroite independent
Mobsupdroite and Stabpelvgauche independent
Mobsupdroite and Stabscap independent
```{r}
#Indépendance entre catégories d'exercices : Mobsupgauche
chisq.test(Mobsupgauche,Mobsupbil)
chisq.test(Mobsupgauche,Stabpelvdroite)
chisq.test(Mobsupgauche,Stabpelvgauche)
chisq.test(Mobsupgauche,Stabscap)
```
Mobsupgauche and Stabpelvdroite independent
Mobsupgauche and Stabpelvgauche independent
Mobsupgauche and Stabscap independent
```{r}
#Indépendance entre catégories d'exercices : Mobsupbil
chisq.test(Mobsupbil,Stabpelvdroite)
chisq.test(Mobsupbil,Stabpelvgauche)
chisq.test(Mobsupbil,Stabscap)
```
Mobsupbil and Stabpelvdroite independent
Mobsupbil and Stabpelvgauche independent
Mobsupbil and Stabscap independent
```{r}
#Indépendance entre catégories d'exercices : Stabpelvdroite
chisq.test(Stabpelvdroite,Stabpelvgauche)
chisq.test(Stabpelvdroite,Stabscap)
```

```{r}
#Indépendance entre catégories d'exercices : Stabpelvgauche
chisq.test(Stabpelvgauche,Stabscap)

#Indépendance entre catégories d'exercices : Stabscap -> fait avec tous les autres tests
```



